$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
Shorten subject reduction a little

\begin{proof}
  By induction on $P \reduce{c} Q$.
  \hfill{}\\
  \begin{itemize}
    \item
    Case $\constr{comm}$: we apply framing (\autoref{thm:framing}) to rearrange the assumptions and then apply substitution (\autoref{thm:substitution}) and strengthening (\autoref{thm:strengthening}).

@@

    \item
    Case $\constr{res}$: reduction under scope restriction case splits on the channel $c$ on which communication occurs.
    If $c$ is $\constr{internal}$ we proceed inductively.
    If $c$ is $\constr{external}\; \constr{0}$ -- i.e. the channel that is being introduced by the scope restriction -- we use \autoref{lm:comm-capable} to subtract $\lio$ from the channel's usage annotation and proceed inductively.
    If $c$ is $\constr{external}\; (\suc i)$ we proceed inductively.

>>>>

\begin{proof}
  By induction on $P \reduce{c} Q$.
  \hfill{}\\
  \begin{itemize}
    \item
    Case $\constr{comm}$: we apply framing (\autoref{thm:framing}) (to rearrange the assumptions), substitution (\autoref{thm:substitution}) and strengthening (\autoref{thm:strengthening}).

@@

    \item
    Case $\constr{res}$: case split on channel $c$:
    if $\constr{internal}$ proceed inductively;
    if $\constr{external}\; \constr{0}$ (i.e. the channel introduced by scope restriction) use \autoref{lm:comm-capable} to subtract $\lio$ from the channel's usage annotation and proceed inductively;
    if $\constr{external}\; (\suc i)$ proceed inductively.
